### 2017-07-24 paper/response.Rmd

- I agree that the rows should be in the order that you see the dataframes. I would also prefer for the column names to be on top of the visualisation - I have now implemented this, although I think that the presentation of the column names is perhaps not as nice.

- The flip argument was placed there to experiment with this idea of flipping the plot - as you suggested, to have row 1 at the top. The flip argument has now been removed, as I cannot now really think of any times where I would prefer the old arrangement of rows.

- I think that the default sort_type option should be to put all of the similar columns together - to me this makes it easier to identify what is similar, and what is different; when I start looking at a dataset I usually want to know what variables are what class. I am willing to change this, however.^

- I agree with you re the palette argument being provided for all plots, although I'm not sure how this could work for vis_miss. But perhaps I should allow for users to insert their own palette for this. Personally I think that there should be a standard palette where the common classes (character, factor, integer, numeric, datetime, etc) each have their own distinct colour, and other classes are given different factors.

@@

> The vis_guess description is a bit hard to follow. I'd start by stating what it does do, before making the comparison to vis_dat, just so it's a bit more self-contained.

- Done, great suggestion!

> The visdat and visdat-package sections are empty, when, I assume, you'll want the description to be included (right now description just says "visdat").

- Thank you for picking up on this, I've updated the main description file now

@@

- This has been implemented for all but `vis_miss_ly` - as this is written in plotly, and I'm not certain how to get it to flip.

# njtierney summary response and remaining tasks to complete

This has been a fantastic process to be a part of. To summarise, the main changes that I made were:

- re-orienting the vis_* family to read in the way that one reads a dataframe
- removing many of the error messages that occur due to some tidy/dplyr collation of factors
- refactoring repeated code into internal functions to more clearly express what was happening, and avoiding repetition. This resulted in the creation of internal functions `vis_gather_`, `vis_extract_value`, and `vis_create_`
- adding percentage missing to the column names in `vis_miss`

- For the moment I have decided to submit visdat to CRAN, with the main functions: 
  - vis_dat
  - vis_miss

Then, in a separate branch, there will be all of the features:
  - vis_compare()
  - vis_guess()
  - vis_*_ly() family

There is still more work to be done on these functions. Specifically:

- vis_guess. This needs to be made much faster, and will incorporate the C code from @seaaan to do so.
- vis_*_ly() family will be written in pure plotly, for speed.

I now summarise some of the changes that I wanted to confirm with the reviewers, @seaaan and @batpigandme:

1. Is the warning message for vis_guess/vis_compare code OK? `example(vis_guess) / example(vis_compare)`

2. The default sort option. I think that the default sort_type option should be to put all of the similar columns together - to me this makes it easier to identify what is similar, and what is different; when I start looking at a dataset I usually want to know what variables are what class. I am willing to change this, however.

3. Maximum row size issue. This is an interesting one! It was brought to my attention [here](https://github.com/njtierney/visdat/issues/32), by @MilesMcBain, but I couldn't replicate this issue. Similarly, I can actually display the nycflights data. So it seems that this is to do with the fact that computations power has a bit to do with it. I think that option 1 is the best case here, but option 2 actually gets a little bit difficult, because this leads to another issue of effectively downsampling a dataset whilst maintaining data structure. This could be a problem, say, if I did perform down-sampling and then the user looked at the data with visdat and plotly, they might get a mis-represented sample. Likewise, if there is a very large proportion of missing data, this might be difficult to preserve exactly. Ways around this might include some very explicit warning messages, or perhaps even a note directly on the plot that the data have been downsampled. ^At the moment one solution forward is to have a check first, something like:

4. Speed for vis_guess. @seaaan wrote some nice code to make this work much much faster, and I think that this is a fantastic idea! But I'm not sure on the best way to move this into production of `visdat`, since it sounds like we would need to borrow a chunk of code from readr and then modify it. I wonder if perhaps the solution here is to do a pull request for this specific feature in `readr`?

5. Can the two issues below be replicated?

### 2017-07-28 README.Rmd
update badges

[![Travis Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)

>>>>

[![Travis Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)
